\documentclass[letterpaper,8pt,twocolumn,twoside,]{pinp}

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% pinp change: the geometry package layout settings need to be set here, not in pinp.cls
\geometry{layoutsize={0.95588\paperwidth,0.98864\paperheight},%
  layouthoffset=0.02206\paperwidth, layoutvoffset=0.00568\paperheight}

\definecolor{pinpblue}{HTML}{185FAF}  % imagecolorpicker on blue for new R logo
\definecolor{pnasbluetext}{RGB}{101,0,0} %



\title{PhD Proposal: Reservation Exchange and Dynamic Pricing \&
Procurement}

\author[a]{Edward Jie Xu}

  \affil[a]{Department of Technology, Management and Economics,
Technical Univeristy of Denmark, Denmark}

\setcounter{secnumdepth}{5}

% Please give the surname of the lead author for the running footer
\leadauthor{}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 

\begin{abstract}
Highlights: @ A continuous double auction market with a new type of
limit order books is proposed to replace incumbent electricity families,
making it possible for small-scale prosumers to directly participate. @
Discrete event simulations of multi-agent systems are used as the main
research tools to demonstrate market operations and decision-making
processes. @ A new decision-making framework based on model predictive
control is introduced to facilitate procurement, control and response of
participants. @ Based on the same idea, a business as retailers can be
started up in incumbent power industries as real-world experiments.
Existing literature in revenue management, inventory management, supply
chain management, etc can be put into use. @ Simulations can provide
statistics for long-term investments, and a new structure for power
systems can emerge, especially in underdeveloped areas. @ The market can
be applied in other industries, like food supply chains, the retailing
and the banking.
\end{abstract}

\dates{This version was compiled on \today} 

% initially we use doi so keep for backwards compatibility
% new name is doi_footer

\pinpfootercontents{Proposal: Rex and DPP}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.


\hypertarget{reference}{%
\section{Reference}\label{reference}}

\begin{itemize}
\tightlist
\item
  \href{https://www.sciencedirect.com/science/article/pii/S0378778811000491}{bacher2011identifying}
  Bacher, P., \& Madsen, H. (2011). Identifying suitable models for the
  heat dynamics of buildings. Energy and Buildings, 43(7), 1511-1522.
\item
  \href{https://www.taylorfrancis.com/books/9780203946558}{birchler2007information}
  Birchler, U., \& Bütler, M. (1999). Information economics. Routledge.

  \begin{itemize}
  \tightlist
  \item
    \emph{How the market aggregates information is discussed in 5
    chapters in part 2. All kinds of deviations of behaviours by later
    self are introduced briefly in chapter 17.}
  \end{itemize}
\item
  \href{https://www.taylorfrancis.com/books/9781315617213}{blok2017introduction}
  Blok, K., \& Nieuwlaar, E. (2016). Introduction to energy analysis.
  Taylor \& Francis. \emph{Figure \texttt{a} is the figure 0.1 on page
  xxv.}
\item
  \href{https://link.springer.com/article/10.1007/s11238-009-9183-x}{brocas2009dynamic}
  Brocas, I. (2011). Dynamic inconsistency and choice. Theory and
  decision, 71(3), 343-364.
\item
  \href{https://www.nature.com/articles/nphys2191}{buchanan2011it}
  Buchanan, M. (2012). It's a (stylized) fact!. Nature Physics, 8(1),
  3-3.
\item
  \href{https://www.sciencedirect.com/science/article/pii/S1364032114005504}{connell2014benefits}
  Pinson, P., \& Madsen, H. (2014). Benefits and challenges of
  electrical demand response: A critical review. Renewable and
  Sustainable Energy Reviews, 39, 686-699. \emph{In section 1-2, the
  necessity of continuous demand response is discussed.}
\item
  \href{https://www.oxfordscholarship.com/view/10.1093/acprof:oso/9780199936243.001.0001/acprof-9780199936243}{foucault2013market}
  Foucault, T., Pagano, M., Roell, A., \& Röell, A. (2013). Market
  liquidity: theory, evidence, and policy. Oxford University Press.
  \emph{How real-world markets work is introduced at the beginning of
  chapter 1. Make- and Take- decisions in LOB markets are discussed in
  chapter 6.}
\item
  \href{https://link.springer.com/chapter/10.1007/BFb0013570}{franklin1997it}
  Franklin, S., \& Graesser, A. (1996, August). Is it an Agent, or just
  a Program?: A Taxonomy for Autonomous Agents. In International
  Workshop on Agent Theories, Architectures, and Languages (pp.~21-35).
  Springer, Berlin, Heidelberg.
\item
  \href{https://link.springer.com/book/10.1007/978-1-4939-9606-3}{gallego2019revenue}
  Gallego, G., \& Topaloglu, H. (2019). Revenue management and pricing
  analysis. Springer, New York.
\item
  \href{https://www.tandfonline.com/doi/abs/10.1080/14697688.2013.803148}{gould2013limit}
  Gould, M. D., Porter, M. A., Williams, S., McDonald, M., Fenn, D. J.,
  \& Howison, S. D. (2013). Limit order books. Quantitative Finance,
  13(11), 1709-1742.
\item
  \href{https://www.tandfonline.com/doi/abs/10.1080/07408179408966604}{heath1994modeling}
  Heath, D. C., \& Jackson, P. L. (1994). Modeling the evolution of
  demand forecasts ITH application to safety stock analysis in
  production/distribution systems. IIE transactions, 26(3), 17-30.
  \emph{MMFEs are not forecasting techniques, but programs to simulate
  the forecast results.}
\item
  \href{https://link.springer.com/book/10.1007/978-3-642-01828-2}{hougaard2009introduction}
  Hougaard, J. L. (2009). An introduction to allocation rules. Springer
  Science \& Business Media.
\item
  \href{https://www.oxfordhandbooks.com/view/10.1093/oxfordhb/9780199844371.001.0001/oxfordhb-9780199844371-e-43}{iori2012agent}
  Iori, G., \& Porter, J. (2012). Agent-based modelling for financial
  markets. Chapter prepared for the Handbook on Computational Economics
  and Finance. \emph{Section 4-2 is about heterogeneous agents with
  market mediated interactions.}
\item
  \href{https://www.pnas.org/content/116/33/16308}{jacome2019power}
  Jacome, V., Klugman, N., Wolfram, C., Grunfeld, B., Callaway, D., \&
  Ray, I. (2019). Power quality and modern energy for all. Proceedings
  of the National Academy of Sciences, 116(33), 16308-16313. \emph{The
  operation of power grids in less-developed areas is different from
  that in developed countries because the systems are not resilient
  enough for lack of responsive generators, large-scale connections,
  regulations, etc.}
\item
  \href{https://ieeexplore.ieee.org/document/867149}{kirschen2000factoring}
  Kirschen, D. S., Strbac, G., Cumperayot, P., \& de Paiva Mendes, D.
  (2000). Factoring the elasticity of demand in electricity prices. IEEE
  Transactions on Power Systems, 15(2), 612-617.
\item
  \href{https://ieeexplore.ieee.org/document/1198281}{kirschen2003demand}
  Kirschen, D. S. (2003). Demand-side view of electricity markets. IEEE
  Transactions on power systems, 18(2), 520-527. \emph{Price spikes in
  electricity markets are discussed in section 2.}
\item
  \href{https://www.wiley.com/en-us/Fundamentals+of+Power+System+Economics\%2C+2nd+Edition-p-9781119213253}{kirschen2018fundamentals}
  Kirschen, D. S., \& Strbac, G. (2018). Fundamentals of power system
  economics. John Wiley \& Sons.

  \begin{itemize}
  \tightlist
  \item
    \emph{Issues associated with retailers are discussed in section 4-3,
    and those with centralized tradings are in section 3-3-3. Why and
    how centralized system operators in incumbent electricity markets
    maintain safety within trading units are discussed in chapter 6.
    However, system operators are expected to be eliminated in this
    project.}
  \end{itemize}
\item
  \href{https://www.tandfonline.com/doi/abs/10.1088/1469-7688/1/2/307}{lebaron2001builder}
  LeBaron, B. (2001). A builder's guide to agent-based financial
  markets. Quantitative finance, 1(2), 254-261. \emph{``It is not really
  a survey, but a kind of view from the trenches in terms of building
  artificial markets.''}
\item
  \href{https://journals.sagepub.com/doi/abs/10.1260/030952405776234599}{madsen2005standardizing}
  Madsen, H., Pinson, P., Kariniotakis, G., Nielsen, H. A., \& Nielsen,
  T. S. (2005). Standardizing the Performance Evaluation of Short-Term
  Wind Power Prediction Models. Wind Engineering, 29(6), 475--489.
\item
  \href{https://www.sciencedirect.com/science/article/pii/S092911990200055X}{maloney2003complexity}
  Maloney, M. T., \& Mulherin, J. H. (2003). The complexity of price
  discovery in an efficient market: the stock market reaction to the
  Challenger crash. Journal of corporate finance, 9(4), 453-479.
  \emph{An empirical event study on how the new knowledge and its
  associated equilibrium price is discovered.}
\item
  \href{https://www.springer.com/gp/book/9781441979988}{nahmias2011perishable}
  Nahmias, S. (2011). Perishable inventory systems (Vol. 160). Springer
  Science \& Business Media.
\item
  \href{https://dl.acm.org/doi/10.1145/2591971.2591982}{nair2014energy}
  Nair, J., Adlakha, S., \& Wierman, A. (2014, June). Energy procurement
  strategies in the presence of intermittent sources. In The 2014 ACM
  international conference on Measurement and modeling of computer
  systems (pp.~85-97).
\item
  \href{https://www.sciencedirect.com/science/article/pii/S037877880700031X}{page2008generalised}
  Page, J., Robinson, D., Morel, N., \& Scartezzini, J. L. (2008). A
  generalised stochastic model for the simulation of occupant presence.
  Energy and buildings, 40(2), 83-98.
\item
  \href{https://www.nature.com/articles/nenergy201632}{parag2016electricity}
  Parag, Y., \& Sovacool, B. K. (2016). Electricity market design for
  the prosumer era. Nature energy, 1(4), 1-6.
\item
  \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1937-5956.2010.01133.x?casa_token=lVRyRU67RhMAAAAA:8Dj0zKFhuT8i_4hkKs0PDvKRC3RUMLWaJk_poEYL7Z9oYcOJVB4-ZsEuT18KN15fuZcrCWLtaAeNayg}{prasad2011advance}
  Prasad, A., Stecke, K. E., \& Zhao, X. (2011). Advance selling by a
  newsvendor retailer. Production and Operations Management, 20(1),
  129-142. \emph{Behaviors of customers are discussed in subsection 3.2}
\item
  \href{https://www.sciencedirect.com/science/article/pii/S0377221710008040}{qin2011newsvendor}
  Qin, Y., Wang, R., Vakharia, A. J., Chen, Y., \& Seref, M. M. (2011).
  The newsvendor problem: Review and directions for future research.
  European Journal of Operational Research, 213(2), 361-374.
\item
  \href{https://sites.engineering.ucsb.edu/~jbraw/mpc/}{rawlings2019model}
  Rawlings, J. B., Mayne, D. Q., \& Diehl, M. (2017). Model predictive
  control: theory, computation, and design (Vol. 2). Madison, WI: Nob
  Hill Publishing. \emph{MPC regulators are introduced in chapter 1.}
\item
  \href{https://www.elsevier.com/books/simulation/ross/978-0-12-415825-2}{ross2012simulation}
  Ross, S. (2012) Simulation. Academic Press.
\item
  \href{https://pubsonline.informs.org/doi/10.1287/msom.2013.0473}{secomandi2014optimal}
  Secomandi, N., \& Kekre, S. (2014). Optimal energy procurement in spot
  and forward markets. Manufacturing \& Service Operations Management,
  16(2), 270-282.
\item
  \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1937-5956.2007.tb00291.x}{shen2007customer}
  Shen, Z. J. M., \& Su, X. (2007). Customer behavior modeling in
  revenue management and auctions: A review and new research
  opportunities. Production and operations management, 16(6), 713-728.
  \emph{Inter-temporal substitutions are discussed in section 2-1.}
\item
  \href{https://www.cambridge.org/core/books/multiagent-systems/B11B69E0CB9032D6EC0A254F59922360}{shoham2009multiagent}
  Shoham, Y., \& Leyton-Brown, K. (2008). Multiagent systems:
  Algorithmic, game-theoretic, and logical foundations. Cambridge
  University Press. \emph{MASs with continuous double auctions are
  discussed in section 11-4.}
\item
  \href{https://journals.sagepub.com/doi/abs/10.1177/109467050023001?casa_token=nHdK2gtk0ZUAAAAA:JZm0jvC2O9C0qr7WPZZphEZINBT2hpYCLNSB5hykwAO1buCHLim0JzlleOeUOwCv0uIZWbmfE8vI}{shugan2000advance}
  Shugan, S. M., \& Xie, J. (2000). Advance pricing of services and
  other implications of separating purchase and consumption. Journal of
  Service Research, 2(3), 227-239. \emph{Elasticities are different
  regarding purchasing for the same asset at different times.}
\item
  \href{https://www.cambridge.org/core/books/how-to-price/27B182881BC668B688F8DA949DF52554}{shy2008how}
  Shy, O. (2008). How to price: a guide to pricing techniques and yield
  management. Cambridge University Press.
\item
  \href{https://www.sciencedirect.com/science/article/pii/S0306261911001668}{siroky2011experimental}
  Široký, J., Oldewurtel, F., Cigler, J., \& Prívara, S. (2011).
  Experimental analysis of model predictive control for an energy
  efficient building heating system. Applied energy, 88(9), 3079-3087.
  \emph{There are two outputs and inputs in the model.}
\item
  \href{https://www.sciencedirect.com/science/article/pii/S1364032119300462}{sousa2019peer}
  Sousa, T., Soares, T., Pinson, P., Moret, F., Baroche, T., \& Sorin,
  E. (2019). Peer-to-peer and community-based markets: A comprehensive
  review. Renewable and Sustainable Energy Reviews, 104, 367-378.
\item
  \href{https://www.nature.com/articles/s41560-019-0346-x}{spyrou2019planning}
  Spyrou, E., Hobbs, B. F., Bazilian, M. D., \& Chattopadhyay, D.
  (2019). Planning power systems in fragile and conflict-affected
  states. Nature Energy, 4(4), 300-310.
\item
  \href{https://pubsonline.informs.org/doi/abs/10.1287/opre.1090.0797?casa_token=ToDJ8Q4lVrwAAAAA:PMHqig45Pa7ai5FpOPhTgs-4U8cI_dbkkScDXU9gZBcPngxvOQnVoEJ_qENYKTfUHjLoVAGiwg}{su2010intertemporal}
  Su, X. (2010). Intertemporal pricing and consumer stockpiling.
  Operations research, 58(4-part-2), 1133-1147. \emph{The rational
  expectations equilibrium is solved with the assumption that all
  players make optimal dynamic decisions given correct beliefs about
  others' behavior, while the communication of information is omitted.}
\item
  \href{https://pubsonline.informs.org/doi/10.1287/mnsc.1090.1075}{su2010optimal}
  Su, X. (2010). Optimal pricing with speculators and strategic
  consumers. Management Science, 56(1), 25-40. \emph{There are four
  different types of consumers coming and going described in section 3.
  Their welfare is not analyzed. Besides, there are only two types of
  consumer valuations. Though there are random variables, the outcomes
  are always assumed to be known to everyone immediately.}
\item
  \href{https://wwnorton.com/books/9780393689983/about-the-book/product-details}{varian2017intermediate}
  Varian, H. R. (2014). Intermediate microeconomics with calculus: a
  modern approach. WW Norton \& Company. \emph{Chapter 3 writes ``it is
  often useful to think of the `same' good available in different
  locations or circumstances as a different good, since the consumer may
  value the good differently in those situations.'' So preferences for
  assets with different leads time are different, and the short-term
  elasticity is expected to decrease as the gate closure approaches.}
\item
  \href{https://pubsonline.informs.org/doi/pdf/10.1287/msom.1120.0387}{wang2012multiordering}
  Wang, T., Atasu, A., \& Kurtuluş, M. (2012). A multiordering
  newsvendor model with dynamic forecast evolution. Manufacturing \&
  Service Operations Management, 14(3), 472-484. \emph{Discrete forecast
  evolutions are used, and there is only one target selling season.
  Instead, continuous updates are required in the CDA market and the
  provision process is discrete over time.}
\item
  \href{https://www.sciencedirect.com/science/article/pii/S0301421509005564}{weber2010adequate}
  Weber, C. (2010). Adequate intraday market design to enable the
  integration of wind energy into the European power systems. Energy
  policy, 38(7), 3155-3163. \emph{Trading volumes in intra-day markets
  in Europe 10 years ago are shown in table 3.}
\item
  \href{https://ieeexplore.ieee.org/document/6262462}{woods2013simulation}
  Woods, M. J., Russell, C. J., Davy, R. J., \& Coppin, P. A. (2012).
  Simulation of wind power at several locations using a measured
  time-series of wind speed. IEEE Transactions on Power Systems, 28(1),
  219-226.
\item
  \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1937-5956.2009.01092.x?casa_token=OFXPwPdWLU0AAAAA:5l-61h0Fl19UbgKSXoJEyS85zUGGyqK8-G6A4TImpG4StMJtsJKjokbC6r4jwvezceSVpybsbpqsZ8A}{zhao2010pre}
  Zhao, X., \& Stecke, K. E. (2010). Pre‐orders for new to‐be‐released
  products considering consumer loss aversion. Production and Operations
  Management, 19(2), 198-215. \emph{Behaviors of customers are discussed
  in subsection 2.2}
\end{itemize}

%\showmatmethods





\end{document}
